### 2016-04-19 thesis/declaration.tex
end
copyright

\item Chapter \ref{ch:mn} has been accepted for publication in \emph{The Astrophysical Journal} as 
``Supermassive black holes and their host spheroids 
III. The $M_{\rm BH} - n_{\rm sph}$ correlation''
by Giulia A.~D.~Savorgnan.

@@

>>>>

\item Chapter \ref{ch:mn} has been published as 
``Supermassive black holes and their host spheroids 
III. The $M_{\rm BH} - n_{\rm sph}$ correlation''
in 2016, ApJ, 821, 88, by Giulia A.~D.~Savorgnan.

@@

I warrant that I have obtained, where necessary, permission from the copyright owners to use 
any third part copyright material reproduced in the thesis, 
or to use any of my own published work in which the copyright 
is held by another party.
